#Statistical Inference Course Project - Part 2

*Li Xin*  
*23 December, 2015*

##Overview
This is the second part of project for the statistical inference class. In this part, ToothGrowth dataset will be loaded and performed some basic exploratory analysis.

##Load Dataset
```{r}
library(datasets)
str(ToothGrowth)
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
```

##Basic Summary

```{r}
summary(ToothGrowth)
```

The below box plot shows tooth length with Dose. We can see there is a big difference there.
```{r}
boxplot(len~dose,data=ToothGrowth,col=c("green","purple","yellow"),
        main="Tooth Length and Dose")
```

The below box plot shows tooth length with supplement type. There are not much difference between these 2 types of supplement.
```{r}
boxplot(len~supp,data=ToothGrowth,col=c("blue","red"),
        main="Tooth Length and Supplement Type")
```

The below box plot shows interaction between dose and supplement type.
```{r}
boxplot(len~interaction(supp,dose),data=ToothGrowth,
        main="Tooth Length and Dose with Supplement",col=sample(rainbow(6)))
```

From the above box plot we can see supplement types increases with the tooth length.

##Confidence Interval & Hypothesis
From the above plots we can assume that for tooth length, there is probably a highly significant difference between dose, and not a significant difference between supplement type.

Below is the T test for supplement type. Then test the effect of supplement type on tooth length when have dose constant at each level.
```{r}
oj <- ToothGrowth[ToothGrowth$supp=="OJ",]
vc <- ToothGrowth[ToothGrowth$supp=="VC",]
oj05 <- oj[oj$dose==0.5,]
oj10 <- oj[oj$dose==1.0,]
oj20 <- oj[oj$dose==2.0,]
vc05 <- vc[vc$dose==0.5,]
vc10 <- vc[vc$dose==1.0,]
vc20 <- vc[vc$dose==2.0,]

#t test vc and oj then dose = 0.5    
vcoj0.5 <- t.test(len~supp,data=rbind(vc05,oj05),var.equal=FALSE)

#t test vc and oj then dose = 1.0 
vcoj1.0 <- t.test(len~supp,data=rbind(vc10,oj10),var.equal=F)

#t test vc and oj then dose = 2.0    
vcoj2.0 <- t.test(len~supp,data=rbind(vc20,oj20),var.equal=F)
```



Here we can see the the summary:
    
For vc and oj at dose=0.5:
the P value is $`r vcoj0.5$p.value`$,
the conf int (-) is $`r vcoj0.5$conf.int[1]`$,
the conf int (+) is $`r vcoj0.5$conf.int[2]`$
    
For vc and oj at dose=1.0:
the P value is $`r vcoj1.0$p.value`$,
the conf int (-) is $`r vcoj1.0$conf.int[1]`$,
the conf int (+) is $`r vcoj1.0$conf.int[2]`$
    
For vc and oj at dose=2.0:
the P value is $`r vcoj2.0$p.value`$,
the conf int (-) is $`r vcoj2.0$conf.int[1]`$,
the conf int (+) is $`r vcoj2.0$conf.int[2]`$
    
    
    
Here we are going to test the effect of dose on tooth length:
    
```{r}
#0.5 vs 1.0
vc0.5and1.0 <- t.test(len~dose,data=rbind(vc05,vc10),var.equal=TRUE)
oj0.5and1.0 <- t.test(len~dose,data=rbind(oj05,oj10),var.equal=TRUE)

#1.0 vs 2.0
vc1.0and2.0 <- t.test(len~dose,data=rbind(vc10,vc20),var.equal=TRUE)
oj1.0and2.0 <- t.test(len~dose,data=rbind(oj10,oj20),var.equal=TRUE)

#0.5 vs 2.0
vc0.5and2.0 <- t.test(len~dose,data=rbind(vc05,vc20),var.equal=TRUE)
oj0.5and2.0 <- t.test(len~dose,data=rbind(oj05,oj20),var.equal=TRUE)
```



Here we can see the summary:
    
For VC 0.5 and 1.0: 
P-value is $`r vc0.5and1.0$p.value`$,
conf int (-) is $`r vc0.5and1.0$conf.int[1]`$,
conf int (+) is $`r vc0.5and1.0$conf.int[2]`$
    
For OJ 0.5 and 1.0:
P-value is $`r oj0.5and1.0$p.value`$,
conf int (-) is $`r oj0.5and1.0$conf.int[1]`$,
conf int (+) is $`r oj0.5and1.0$conf.int[2]`$
    
For VC 1.0 and 2.0:
P-value is $`r vc1.0and2.0$p.value`$,
conf int (-) is $`r vc1.0and2.0$conf.int[1]`$,
conf int (+) is $`r vc1.0and2.0$conf.int[2]`$
    
For OJ 1.0 and 2.0:
P-value is $`r oj1.0and2.0$p.value`$,
conf int (-) is $`r oj1.0and2.0$conf.int[1]`$,
conf int (+) is $`r oj1.0and2.0$conf.int[2]`$
    
For VC 0.5 and 2.0:
P-value is $`r vc0.5and2.0$p.value`$,
conf int (-) is $`r vc0.5and2.0$conf.int[1]`$,
conf int (+) is $`r vc0.5and2.0$conf.int[2]`$
    
For OJ 0.5 and 2.0:
P-value is $`r oj0.5and2.0$p.value`$,
conf int (-) is $`r oj0.5and2.0$conf.int[1]`$,
conf int (+) is $`r oj0.5and2.0$conf.int[2]`$
    
##Conclusion
    
From the analysis above, we can conclude there is a definite dependence on the dose level on tooth growth. P-value are less than threhold and confidence intervals don't include zero. This indicate that when supplement dose increase, the tooth growth will increase significantly.

